---
title: "Developing Data Products Week 2 Assignment"
author: Carolina San Martín
output: 
        ioslides_presentation:
                smaller: true
                widescreen: true
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This project is part of the week 2 assignment of the course “Develpoing Data Products” of Data Science specialization with R from Johns Hopkins University. The aim of this project is to create a webpage that contains a map created with leaflet package.

```{r packages, error=FALSE, message=FALSE, warning=FALSE}

# Packages used in this report
packages <- c("knitr","dplyr","leaflet")
for (p in packages) {
        if (!require(p,character.only = TRUE)){install.packages(p)}; 
        library(p,character.only = TRUE)
}   

``` 

## Submission
This webpage presents the locations of some of the best universities in Chile to study a bachelor in computer sciences. The popups will show the name of the university.

Note: Google map was the unique source of information :)


## Mapping
```{r places, echo=TRUE, out.width = '50%'}
map <- leaflet(height = 280, width = 700) %>% addTiles() %>%  
        addMarkers(lat = -33.457737, lng = -70.664718, popup = "University of Chile - Department 
                   of Computer Sciences") %>% 
        addMarkers(lat = -33.496518, lng = -70.607781, popup = "Pontifical Catholic University of Chile -
                   Department of Computer Sciences") %>% 
        addMarkers(lat = -33.034718, lng = -71.596716, popup = "Federico Santa María Technical University -
                   Department of Informatics") %>% 
        addMarkers(lat = -36.830859, lng = -73.036740, popup = "University of Concepción -  Department 
                   of Computer Science")
map
```


## Mapping Clusters
To try the mapping clusters, create a data frame with a simulation of coordenates based on the places preented in previous plot. When you zoom in to each cluster, the cluster will seperate until you see the individual Markers.


## Clusters around Chile
```{r clusters, echo=TRUE}
df <- data.frame(lat=runif(300, min = -36.830859, max = -33.034718),
                 lng=runif(300, min = -73.036740, max = -70.607781))  
df %>%
leaflet(height = 350, width = 700) %>%
addTiles() %>%  
addMarkers(clusterOptions = markerClusterOptions()) 
```

