---
title: "Developing Data Products"
subtitle: "Week 3 Assignment"
author: Carolina San Martín
output: 
        ioslides_presentation:
                smaller: true
                widescreen: true
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This project is part of the week 3 assignment of the course “Develpoing Data Products” of Data Science specialization with R from Johns Hopkins University. The aim of this project is to create a webpage that contains plots using plotly.

So I made two interactive plots using plotly and two datasets: mtcars (which comes with the dplyr package, also contained in tidyr package) and EuroStockMarket.

```{r packages, error=FALSE, message=FALSE, warning=FALSE}
# Packages used in this report
packages <- c('knitr','tidyr','magrittr','plotly')
for (p in packages) {
        if (!require(p,character.only = TRUE)){install.packages(p)}; 
        library(p,character.only = TRUE)
}   

``` 


## A quick example
```{r pressure, echo=TRUE, message=FALSE, warning=FALSE, fig.align='right',fig.height=4}
mtcars %<>% mutate(cyl = as.factor(cyl))
plot_ly(mtcars, x = ~wt, y = ~mpg, mode = 'markers', color = ~cyl, size = ~hp) %>%
  layout(xaxis = list(title = 'Weight (1000 lbs)'),
         yaxis = list(title = 'Miles/(US) gallon'))
```

## 3D example
```{r 3d, echo=TRUE, message=FALSE, warning=FALSE, fig.align='center',fig.height=4}
mtcars %<>% mutate(vs = ifelse(vs==0,'V-shaped','Straight'),vs = factor(vs, levels = c('V-shaped','Straight')))
plot_ly(mtcars, x = ~wt, y = ~hp, z = ~qsec, color = ~vs) %>% add_markers() %>% 
        layout(scene = list(xaxis = list(title = 'Weight (1000 lbs)'), 
                            yaxis = list(title = 'Gross horsepower'), zaxis = list(title = '1/4 mile time')),
               annotations = list(x = 1.13, y = 1.05, xref = 'paper', yref = 'paper',
                        showarrow = FALSE, text = 'Engine'))
```


## Another example using EurostockMarkets data
```{r eurostock, echo=TRUE, message=FALSE, warning=FALSE, fig.align='center',fig.height=4}
data("EustockMarkets")
stocks <- as.data.frame(EuStockMarkets) %>% 
        gather(index, price) %>% 
        mutate(time = rep(time(EuStockMarkets),4))
plot_ly(stocks, x = ~time, y = ~price, color = ~index)
```